What if you drop that? Modeling children's curiosity about physical interactions

### 2020-01-24 paper/paper.Rmd
worked on tower task analysis

>>>>

### Tower Task

1. height x continuous age
First we examine tower height as a function of age. Y/N we find tower height increases with age.
```{r}
cor.test(hum$height_tallest, hum$age_rounded)
```

```{r, include=F} 
ch_height <- hum %>% group_by(age_group, height_tallest) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

ggplot(ch_height, aes(x=age_group, y=height_tallest)) + 
  geom_smooth(method="lm", level=0.90) + geom_point(alpha=.8, aes(size=n)) +
  scale_shape_manual(values=10:19) +
  xlab("Age") + ylab("Height_Tallest") + ylim(0,10) +
  langcog::scale_fill_solarized() + ggthemes::theme_few()
```

<!-- We find that towers vary in i) height, ii) stacks, and iii) components.  -->

<!-- 1. height x age -->
<!-- -First we examine tower height, of the tallest stack, as a function of age. We find tower height increases with age (cor.test).  -->

<!-- 2a. number stacks x age -->
<!-- -Number of stacks y/ n correlate with age. -->
<!-- -what is "cool": younger and use of horizontal/adjacent tower building -->

<!-- 2b. number collapses x age = intuitive physics (tower stability) -->
<!-- -Hight and number of stacks due to stability issue. -->
<!-- -Number of collapses -->

<!-- 3. The structural components of the towers -->
<!-- -support x supported -->
<!-- -drop object probabilities correlate with objects used in tower? -->
<!-- -first base selection as proxy of most interesting object  -->
<!-- - base and top distribution  -->
